---
title: "Lab 10"
author: "Tiffany Hanratty"
date: "11/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.
Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.

Note, the paper, the data, and an existing reproducible analysis of this data is available at https://crumplab.github.io/statisticsLab/lab-10-factorial-anova.html#important-stuff-4

The re-analysis should focus only on Experiment 3. There are three main goals

1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note, the authors reported a 2x2 repeated measures ANOVA, but consider how the same questions could be answered by t-tests (2 points)

```{r}
library(papaja)
library(dplyr)
library(ggplot2)
 
all_data <- read.csv("open_data/stroop_stand.csv")

(stand_stroop <- t.test(all_data$incongruent_stand,
                        all_data$congruent_stand,
                        paired = TRUE))

(sit_stroop <- t.test(all_data$incongruent_sit,
                        all_data$congruent_sit,
                        paired = TRUE))

```
Confidence:

2. Reproduce a graph of the means, like shown in the paper (2 points)

```{r}
library(tidyr)

stroop_df <- all_data %>%
  pivot_longer(cols = 1:4,
               names_to = c("Congruency","Posture"),
               names_sep = "_",
               values_to = "RTs")

overall_means <- stroop_df %>%
            group_by(Posture, Congruency) %>%
            summarise(mean_RT = mean(RTs),
                      SEMRT = sd(RTs)/sqrt(length(RTs)))

ggplot(overall_means, aes(x=Posture, 
                          y=mean_RT, 
                          group=Congruency, 
                          fill=Congruency))+
  geom_bar(stat="identity", position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Reaction Time (ms)")+
  geom_errorbar(aes(ymin=mean_RT-SEMRT, 
                    ymax=mean_RT+SEMRT), 
                position=position_dodge(width=0.9),
                width=.2)+
  coord_cartesian(ylim=c(500,1000))

```
Confidence:

3. Present a power-curve analysis for the design. (2 points)

```{r}
effect_sizes <- seq(0,1.5,.1)
prop_significant <-c()

for(i in 1:length(effect_sizes)){
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value,
                                   
                              
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
  
}



plot_df <- data.frame(effect_sizes,
                      prop_significant)

ggplot(plot_df, aes(x=effect_sizes,y=prop_significant))+
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks=seq(0,1.5,.1))+
  scale_y_continuous(breaks=seq(0,1,.1)) +
  ylab("Proportion Significant")


```
Confidence:



