---
title: "Lab 11"
author: "Tiffany Hanratty"
date: "12/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
X <- c(1,4,3,2,5,4,3,6,7,8)
Y <- c(1,3,6,7,8,2,8,7,6,9)

```

An X and Y variable contain the above numbers.

1. 
A. Compute Pearson’s r and report the associated p-value using the cor.test() function. (2 points)

```{r}
(my_cor <- cor.test(X,Y))

```
The correlation was $r$ = `r round(my_cor$estimate,digits=2)`, $p$ - `r round(my_cor$p.value,digits=2)`

Confidence: 100

B. Use a permutation test to create a null-distribution, and report the p-value for getting the observed correlation or larger using your simulated null-distribution. (2 points)

```{r}
sim_rs <- replicate(1000,cor(sample(X),sample(Y)))
hist(sim_rs)

length(sim_rs[sim_rs >= cor(X,Y)])/1000

```
Confidence: 85


2. Using the variables X and Y above, and assuming that the values could be re-ordered in any way, report the following:

A. the smallest possible sum of products (1 point)

```{r}

sort(X)
sort(Y, decreasing = TRUE)

sum(sort(X)*sort(Y, decreasing = TRUE))

```
Confidence: 85

B. the largest possible sum of products (1 point)

```{r}
sum(sort(X)*sort(Y))

```

Confidence: 90






