---
title: "Lab 7"
author: "Tiffany Hanratty"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. A test-taker answered 50 true/false questions and received a score of 60% correct. Report the results of a binomial test and explain whether you think the test-score could be produced by the test-taker randomly guessing on each question. (2 points)

```{r}
binom.test(x = 30,
           n = 50,
           p = .5)


```
Based on the data, there is a 20.26% chance the test-taker received a 60% on the test by randomly guessing. I think this test score could be produced by randomly guessing, but I would consider it fairly unlikely. A 20.26% chance of the test-taker getting 60% on the test by randomly guessing just seems a bit low for me to think it would be highly probable they were just guessing on each answer. Though I think getting this score by randomly guessing is an unlikely scenario, I would not completely rule it out as a possibility. 

Confidence: 75



2. An examiner wants to make a TRUE/FALSE test, but is still deciding how many questions they will include. They want to make sure that it would be very difficult to simply randomly guess and be able to score any higher than 55% percent. How many questions would the examiner need to use to be confident that scores of 55% or higher were not produced by chance? (2 points)

```{r}
binom.test(x = 165,
           n = 300,
           p = .5,
           alternative="greater")
```
I think it would be a safe bet for the examiner to use 300 questions to ensure scores of 55% or higher were not produced by chance. Using 300 questions would leave a 4.7% chance that a score of 55% or higher was obtained by chance. Considering this is quite a low percentage, and does not seem very likely to happen, I think the examiner should feel relatively confident about the use of 300 questions. 

Confidence:70

3. A test has 5 TRUE/FALSE questions (each with one right answer) and 5 multiple choice questions with four choices each (each with only one right answer).

- create a sampling distribution or probability distribution to illustrate how a random chance process could perform on this test. (1 point)

```{r}
rbinom(n = rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25))

simulated_test <- replicate(10000, rbinom(n = rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25)) )

simulated_scores <- colSums(simulated_test)/10

library(ggplot2)

qplot(simulated_scores)+
  geom_histogram()

length(simulated_scores[simulated_scores > .75])/10000

sum(rbinom(n = rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25)))

s_distribution <- replicate(10000,sum(rbinom(n = rep(1,10), size = 1, prob = c(.5,.5,.5,.5,.5,.25,.25,.25,.25,.25))) )

hist(s_distribution)
           
```

Confidence:50

- What is the probability that randomly guessing on each question could allow a person to receive 75% or greater on this test? (1 point)

```{r}
s_distribution[s_distribution >= 8]

length(s_distribution[s_distribution >= 8])

length(s_distribution[s_distribution >= 8])/10000
```

Confidence: 55


