---
title: "Lab 8"
author: "Tiffany Hanratty"
date: "11/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of z-scores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

- Advanced: Have an option so that the function will convert the raw scores to z-scores in one of two ways:
- using user provided mean and standard deviation
- using the calculated mean and standard deviation from the raw scores

```{r}

to_zscores_b <- function(raw, mu = NULL, sdev = NULL){
  if(is.null(mu) == TRUE) mu <- mean(raw)
  if (is.null(sdev) == TRUE) sdev <- sd(raw)
  zscores <- (raw-mu)/sdev
  return(zscores)
}

some_numbers <- c(1,2,3,4,5)

to_zscores_b(some_numbers, mu = 5, sdev=1)

to_zscores_b(some_numbers)

```
Confidence: 30

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).
- Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}
z.test <- function(sample_mean, sample_size, mu, sigma){
  smpl_dist_mean <- mu
  smpl_dist_sd <- sigma/sqrt(sample_size)
  
  p_value <- pnorm(sample_mean, smpl_dist_mean, smpl_dist_sd, lower.tail=FALSE)
  return(p_value)
}

z.test(sample_mean = 50,
       sample_size = 25,
       mu = 40,
       sigma = 7)



```

Using the data provided for this z-test, you would get a p-value of 4.57e-13. This means the occurrence of getting a sample mean of greater than 50 with the data set provided would be rather unlikely considering the very small p-value. 
Confidence: 35

