---
title: "Reproducible Report"
author: "Tiffany Hanratty"
date: "12/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
This report consists of a re-analysis of the training portion found in Holmes, To, & Johnsrude (2021).

The article citation is: Holmes, E., To, G., & Johnsrude, I. S. (2021). How Long Does It Take for a Voice to Become Familiar? Speech Intelligibility and Voice Recognition Are Differentially Sensitive to Voice Training. Psychological science, 32(6), 903–915. https://doi.org/10.1177/0956797621991137


The data for this reproducible report were downloaded from https://osf.io/7kdyc/


## Re-analysis

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(papaja)

all_data <- read.csv("SemesterProject/Training_PercentCorrect_(n=50).csv")

(match_1 <- t.test(all_data$fam_1,
                  all_data$fam_2,
                  paired = TRUE))

(match_2 <- t.test(all_data$fam_1,
                  all_data$fam_3,
                  paired = TRUE))

(match_3 <- t.test(all_data$fam_2,
                  all_data$fam_3,
                  paired = TRUE))

                


```

## Table of Means

```{r}
library(tidyr)

fam_df <- all_data %>%
  pivot_longer(cols = 1:3,
               names_to = c("name", "value"),
               names_sep = "_",
               values_to = "RTs")
  


overall_means <- fam_df %>%
  group_by(value, name) %>%
  summarise(meanRT = mean(RTs),
            SEMRT = (sd(RTs)/sqrt(length(RTs))))

knitr::kable(overall_means)

```

## Graph of Means

```{r}
ggplot(overall_means, aes(x=name,
                          y=meanRT, 
                          group=value,
                          fill=value))+
  geom_bar(stat="identity",position="dodge")+
  theme_classic(base_size=12)+
  ylab("Mean Voice Familiarity Performance by group")+
  geom_errorbar(aes(ymin=meanRT-SEMRT,
                    ymax=meanRT+SEMRT),
                position=position_dodge(width=0.9),
                width=.2,
                color="black")+
  coord_cartesian(ylim=c(3,100))


```

## Results 

A paired t-test was used to compare familiarity conditions with performance. Better performance was seen in the most familiar condition  compared to the moderately familiar condition, t(49) = 4.29, p < .001 (Holmes, To, and Johnsrude, 2021). There was also better performance seen in the most familiar condition compared to the least familiar condition,  t(49) = 3.56, p = .001 (Holmes, To, and Johnsrude, 2021). There was not a significant difference found in the moderately familiar group compared to the least familiar group, t(49) = 0.16, p = .88. The confidence interval values were not able to be reproduced in this reanalysis. 



## Discussion

In this re-analysis of the triang portion of Holmes, To, & Johnsrude (2021), t-test values, as well as, p-values for each comparison condition matched those reopeted in the original article. 




